The 18.821 Mathematics Project Lab Report [Proofs]

### 2013-09-28 paper.tex
Argmin and argmax command definitions.
Formatting of equation.
Uniqueness of fastest path.

% Define abs norm, paren, bracket, cbracket, and innerproduct
\usepackage{mathtools}
\DeclarePairedDelimiter\tempabs{\lvert}{\rvert}
\DeclarePairedDelimiter\tempnorm{\lVert}{\rVert}
\DeclarePairedDelimiter\tempinnerproduct{\langle}{\rangle}
\DeclarePairedDelimiter\tempparen{(}{)}
\DeclarePairedDelimiter\tempbracket{[}{]}
\DeclarePairedDelimiter\tempcbracket{\{}{\}}

@@

\begin{definition}
  A valid targetted path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some point mass $p$, conditions $\mathrm{C}$, starting point $\vec{x_1}$, and ending point $\vec{x_2}$ is a valid path where $\gamma(t) = \vec{x_1}$ and $\gamma(T_f(\gamma)) = \vec{x_2}$. In other words, it is a valid path which starts at $\vec{x_1}$ and ends at $\vec{x_2}$.
\end{definition}

\begin{definition}
  A fastest path $\hat{\gamma}: \mathrm{R} \to \mathrm{R}^2$ for a particular point mass $p$, a starting point $\vec{x_1}$, a destination point $\vec{x_2}$, and some set of conditions $\mathrm{C}$ is a valid targetted path $\hat{\gamma}$ such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid targetted paths $\gamma$ with the same $p$, $\vec{x_1}$, $\vec{x_2}$, and $\mathrm{C}$.
\end{definition}

  \begin{theorem}
  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a point mass $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
  \begin{eqnarray}
    y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
  \end{eqnarray}
\end{theorem}
\proof Let's transform the problem. We can reset our coordinate axes so that $(x_1, y_1)$ is set to the origin and $(x_2, y_2)$ is on the x-axis. In this new coordinate system, we have transformed the following:
\begin{eqnarray}
  (x_1, y_1) &\to& (0,0) \\
  (x_2, y_2) &\to& (x_2', 0)
\end{eqnarray}

@@

\begin{corollary}
  The fastest path between two points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ is unique.
\end{corollary}

@@

Since we've proven this lemma, we can invoke it upon $\min l_3 + l_4$. Since $l_3 = \sqrt{z_3}$ and $l_4 = \sqrt{z_4}$, we can use $k(t) = \sqrt{t}$ and we can write $\min l_3 + l_4 = \min z_3 + z_4$ by using our lemma. Thus, we now want to solve the problem:
\begin{eqnarray}
  \argmin_{\theta} 2 \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 + \left( d - \frac{l_2}{2} \cos \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2
\end{eqnarray}

@@

>>>>

% Define abs norm, paren, bracket, cbracket, and innerproduct
\usepackage{mathtools}
\DeclarePairedDelimiter\tempabs{\lvert}{\rvert}
\DeclarePairedDelimiter\tempnorm{\lVert}{\rVert}
\DeclarePairedDelimiter\tempinnerproduct{\langle}{\rangle}
\DeclarePairedDelimiter\tempparen{(}{)}
\DeclarePairedDelimiter\tempbracket{[}{]}
\DeclarePairedDelimiter\tempcbracket{\{}{\}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\begin{definition}
  A valid targetted path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some particle $p$, conditions $\mathrm{C}$, starting point $\vec{x_1}$, and ending point $\vec{x_2}$ is a valid path where $\gamma(t) = \vec{x_1}$ and $\gamma(T_f(\gamma)) = \vec{x_2}$. In other words, it is a valid path which starts at $\vec{x_1}$ and ends at $\vec{x_2}$.
\end{definition}

\begin{definition}
  A fastest path $\hat{\gamma}: \mathrm{R} \to \mathrm{R}^2$ for a particular particle $p$, a starting point $\vec{x_1}$, a destination point $\vec{x_2}$, and some set of conditions $\mathrm{C}$ is a valid targetted path $\hat{\gamma}$ such that $T_f(\hat{\gamma}) \leq T_f(\gamma)$ for all valid targetted paths $\gamma$ with the same $p$, $\vec{x_1}$, $\vec{x_2}$, and $\mathrm{C}$.
\end{definition}

  \begin{theorem}
  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ follows the straight line where all coordinates $(x,y)$ on the straight line are given by:
  \begin{eqnarray}
    y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1
  \end{eqnarray}
\end{theorem}
\proof Let's transform the problem. We can reset our coordinate axes so that $(x_1, y_1)$ is set to the origin and $(x_2, y_2)$ is on the x-axis. In this new coordinate system, we have transformed the following:
\begin{eqnarray}
  (x_1, y_1) &\to& (0,0) \\
  (x_2, y_2) &\to& (x_2', 0)
\end{eqnarray}

@@

\begin{corollary}
  Given points $(x_1, y_1), (x_2, y_2) \in \mathrm{R}^2$ and a particle $p$ whose initial position is $(x_1, y_1)$ which moves with acceleration bounded by $\bar{a}$, the fastest path $\hat{\gamma}(t)$ which $p$ can trace from $(x_1, y_1)$ to $(x_2, y_2)$ is unique.
\end{corollary}
\proof We have already shown that any fastest path between $(x_1, y_1)$ and $(x_2, y_2)$ follows the straight line given by $y = \frac{y_2 - y_1}{x_2 - x_1} x + y_1$. Moreover, we showed that when travelling along the fastest path, the particle must have acceleration along the straight line of $\bar{a}$. Since we have starting position $(x_1, y_1)$ and initial speed of $0$, the acceleration of the particle $a(t)$ uniquely defines a path for the particle.

There is only a single function $a(t) = \bar{a}$ which the acceleration can satisfy when the particle is moving along a fastest path, therefore, there is only a single possible fastest path.
\qed

@@

Since we've proven this lemma, we can invoke it upon $\min l_3 + l_4$. Since $l_3 = \sqrt{z_3}$ and $l_4 = \sqrt{z_4}$, we can use $k(t) = \sqrt{t}$ and we can write $\min l_3 + l_4 = \min z_3 + z_4$ by using our lemma. Thus, we now want to solve the problem:
\begin{eqnarray}
  \argmin_{\theta} &2& \left(\frac{l_1}{2} - \frac{l_2}{2} \sin \theta \right)^2 \\
  &+& \left( d - \frac{l_2}{2} \cos \theta \right)^2 + \left( d + \frac{l_2}{2} \cos \theta \right)^2
\end{eqnarray}

@@

\subsection{Non-Symmetric Quadrilateral}
